Hydra Battles and Cie

### 2021-08-02 doc/part-hydras.tex
chapter 2 (with alectryon) completed
Note: there remain a few Coqnswer blocks (due to a bad display of sub-goals)

\begin{Coqsrc}
Definition Alive (B : Battle) :=
  forall i h, 
     h <> head -> {h' : Hydra |  B i h h'}.
\end{Coqsrc}

@@

\begin{Coqsrc}
Theorem Alive_free: Alive free.

Theorem Alive_standard: Alive standard.  
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition  next_round_dec n :
 forall h, (h = head) + {h' : Hydra & {R1 h h'} + {R2 n h  h'}}.
\end{Coqsrc}

@@

The termination of all battles is naturally expressed by the predicate \texttt{well\_founded} defined in the module \href{https://coq.inria.fr/distrib/current/stdlib/Coq.Init.Wf.html}{Coq.Init.Wf} 
 of the Standard Library.

@@

\begin{Coqsrc}
Definition Termination :=  well_founded (transp _ round).
\end{Coqsrc}

@@

\index{hydras}{Library Hydra!Type classes!Hvariant}
\begin{Coqsrc}
Class Hvariant {A:Type}{Lt:relation A}(Wf: well_founded Lt)(B : Battle)
  (m: Hydra -> A):   Prop :=
  {variant_decr: forall i h h',
      h <> head ->
      battle_rel  B i  h h' -> Lt (m h') (m h)}.
\end{Coqsrc}

@@

\begin{exercise}
 Prove that, if there is an instance of (\texttt{Hvariant Lt wf\_Lt $B$ $m$}), then there exists no infinite battle in  $B$.
\end{exercise}

@@

\begin{Coqsrc}
Section Impossibility_Proof.
 Variable m : Hydra -> nat.
 Hypothesis Hvar : Hvariant lt_wf free m.
\end{Coqsrc}

@@

  \begin{Coqsrc}
  Let iota (i: nat) := hyd_mult head (S i).    
  \end{Coqsrc}

@@

 \begin{Coqsrc}
  Let big_h := hyd1 (hyd1 head).
 \end{Coqsrc}

@@

  \begin{Coqsrc}
 Let small_h := iota (m big_h).

 Fact big_to_small : big_h -1-> small_h.
 Proof.
      exists (m big_h); right; repeat constructor.     
 Qed.
    \end{Coqsrc}

@@

 \begin{Coqsrc}
Lemma m_lt : m small_h < m big_h.
 \end{Coqsrc}

@@

\begin{Coqsrc}
Lemma m_ge : forall i:nat, i <= m (iota i).
\end{Coqsrc}

@@

 Then our proof is almost finished.

   \begin{Coqsrc}
Theorem Contradiction : False.
Proof.
 apply (Nat.lt_irrefl (m big_h));
   apply  Lt.le_lt_trans with (m small_h).
  - apply m_ge.
  - apply m_lt.
Qed.

>>>>

\input{movies/snippets/Hydra_Definitions/AliveDef}

@@

\input{movies/snippets/Hydra_Theorems/AliveThms}

@@

\input{movies/snippets/Hydra_Lemmas/nextRoundDec}

@@

The termination of \emph{any}  battle is naturally expressed by the predicate \texttt{well\_founded} defined in the module \href{https://coq.inria.fr/distrib/current/stdlib/Coq.Init.Wf.html}{Coq.Init.Wf} 
 of the Standard Library.

@@

\input{movies/snippets/Hydra_Definitions/TerminationDef}

@@

\index{hydras}{Library Hydra!Type classes!Hvariant}

\input{movies/snippets/Hydra_Definitions/HvariantDef}

@@

\begin{exercise}
 Prove that, if there exists some  instance of (\texttt{Hvariant Lt wf\_Lt $B$ $m$}), then there exists no infinite battle in  $B$.
\end{exercise}

@@

\input{movies/snippets/Omega_Small/omegaSmalla}

@@

\input{movies/snippets/Omega_Small/iotaDef}

@@

\input{movies/snippets/Omega_Small/bigHDef}

@@

\input{movies/snippets/Omega_Small/smallHDef}

@@

\input{movies/snippets/Omega_Small/mLt}

@@

\input{movies/snippets/Omega_Small/mGea}

\begin{Coqanswer}
1 subgoal (ID 23)
  m : Hydra -> nat
  Hvar : Hvariant lt_wf free m

  small_h := iota (m big_h) : Hydra
  ============================
  forall i : nat, i <= m (iota i)
\end{Coqanswer}

@@

We are now ready to complete our impossibility proof.

\input{movies/snippets/Omega_Small/mGeb}

\input{movies/snippets/Omega_Small/omegaSmallz}
